---
title: "Deep pseudo"
output: html_document
date: 
---
```{r}
library(reticulate)
```

```{python}
import keras
import tensorflow as tf
from tensorflow.python.keras.layers import Input, Dense
from keras.models import Model, load_model
import pandas as pd
import numpy as np
```

```{r}
library(tensorflow)
getOption("max.print")
#rm(list=ls())
library(keras)
library(pseudo)
library(survivalROC)
library(survival)
library(survcomp)
library(survAUC)
library(reticulate)
library(torch)
library(data.table)
library(tidyverse)
library(reticulate)
library(tensorflow)
library(keras)
library(coxphw)
library(Hmisc)
library(SemiCompRisks)
library(rms)
```


```{r}
getPseudoConditional <- function(t, d, qt){
  #browser()
  s <- c(0, qt)  
  n=length(t)
  ns=length(s)-1  # the number of intervals
  D <- do.call(cbind, lapply(1:ns, function(j)  (s[j] < t) * (t <= s[j+1]) * (d == 1)))
  R <- do.call(cbind, lapply(1:ns, function(j) ifelse(s[j] < t, 1, 0)))
  Delta<-do.call(cbind, lapply(1:ns, function(j) pmin(t,s[j+1])-s[j]))
  
  
  # format into long formate
  dd.tmp=cbind.data.frame(id=rep(1:n,ns),s=rep(c(0,qt[-length(qt)]), each=n), y=c(R*Delta),d=c(D))
  
  dd=dd.tmp[dd.tmp$y>0,]
  pseudost=rep(NA, nrow(dd))
  for (j in 1:ns){
    index= (dd$s==s[j])
    dds=dd[index,]
    pseudost[index]=pseudosurv(time=dds$y, event=dds$d, tmax=s[j+1]-s[j])$pseudo
    print(j)
  }
  dd$pseudost=pseudost  
  return(dd[,c(1,2,5)])
}

```

#----------------------------------------------------------------------------------------
# Another example of a neural network with one hidden layer implemented in R keras in the paper
#-----------------------------------------------------------------------------------------
pseudoDNN.train <- function(x_train, y_train){
  
  model <- keras_model_sequential() %>%
    layer_dense(units = 64, kernel_regularizer = regularizer_l2(0.0001), activation = "relu",
                input_shape = dim(x_train)[[2]]) %>%
    layer_dense(units = 32, kernel_regularizer = regularizer_l2(0.01),
                activation = "relu") %>%
        layer_dense(units = 16, kernel_regularizer = regularizer_l2(0.01),
                activation = "relu") %>%
    layer_dense(units = 8, kernel_regularizer = regularizer_l2(0.01),
                activation = "relu") %>%
    layer_dense(units = 1, activation='sigmoid')
  
  model %>% compile(
    optimizer =optimizer_adamax(learning_rate = 0.0025),
    loss = "mse",
    metrics = c("mae")
  )
  model %>% fit(x_train, y_train,
                epochs = 1000, batch_size = 64,
                verbose = 0)
  
  model
}
#----------------------------------------------------------------------------
#prediction based on a keras model
#----------------------------------------------------------------------------
pseudoDNN.predict <- function(model, x_test){
  ypred <- model %>% predict(x_test)
  }

```

```{r}
Deep = list()
CoxM =list()
for (i  in 1:10) {
data("pbc", package = "survival")
head(pbc)[, c(1:5, 11, 12)]
head(pbcseq)[, c(1, 4:5, 7, 12, 13)]
pbc <- pbc %>% mutate(bili = log(bili), protime = log(protime),alk.phos)
pbcseq <- pbcseq %>% mutate(bili = log(bili), protime = log(protime),alk.phos=log(alk.phos))

temp <- subset(pbc, id <= 312, select = c(id:sex)) # baseline
pbc2 <- tmerge(temp, temp, id = id, death = event(time, status)) #set range
pbc2 <- tmerge(pbc2, pbcseq, id = id, bili = tdc(day, bili),
               protime = tdc(day, protime), alk.phos=tdc(day,alk.phos))
pbc2<-pbc2%>%  mutate( time_period= case_when(tstop >= 1  & tstop <= 2000 ~ '1',
                                    tstop >= 2001  & tstop <= 2440 ~ '2',
                                    tstop >= 2441  ~ '3'))

rf_data_melt<- pivot_longer(pbc2, c(bili,protime,alk.phos),names_to = "variable", values_to = "value")
head(rf_data_melt)

dodge <- position_dodge(width = 0.4)
options(repr.plot.width=13, repr.plot.height=8)
ggplot((rf_data_melt %>% filter( variable == "bili"|variable == "protime"|variable=="alk.phos") %>% drop_na()),
       aes(x=factor(time_period),y=value,fill=variable))+geom_boxplot()+labs( x = "Time period")

# Split the data into train and test 
pbc2$status<-ifelse(pbc2$status==2, 1, 0)
split<-split(pbc2, f = pbc2$id>=200) 

train <-split$`FALSE`
test <-split$`TRUE`

# Response 
surv_train <- train$tstop
cen_train <- train$status

surv_test <- test$tstop
cen_test <- test$status

fitpbc <- cph(Surv(tstart, tstop, status) ~protime+bili+age+sex+trt+alk.phos, train, x=T, y=T)
#summary(fitpbc)
valfitpbc<-validate(fitpbc,method="boot", B=20,dxy=TRUE, data=test)


# covariates

x_train<- train[,c(4,5,6,10,11,12)]

x_test<-test[,c(4,5,6,10,11,12)]
x_train_cont<-x_train[,c(2,4,5,6)]
x_test_cont<-x_test[,c(2,4,5,6)]
## Normalise data
min_max_norm <- function(x) {
  (x - min(x)) / (max(x) - min(x))
}

x_train_norm<-min_max_norm(as.matrix(x_train_cont))
x_test_norm<-min_max_norm(as.matrix(x_test_cont))

pickTime<-c(2000, 2440,3880)
x_train<-cbind(x_train_norm,x_train[,c(1,3)])
x_test<-cbind(x_test_norm,x_test[,c(1,3)])
pseudo <- pseudosurv(time=surv_train,event=cen_train,tmax=pickTime)

btrain <- NULL
for(it in 1:length(pseudo$time)){
  btrain <- rbind(btrain,cbind(train,pseudo = pseudo$pseudo[,it],
                               tpseudo = pseudo$time[it],id=1:nrow(train)))
}

train <- btrain


# create dummy variables for the time points
smatrix=model.matrix(~as.factor(train$tpseudo)+0)
x_train<-cbind(x_train_norm,x_train[,c(1,3)])
#create input predictors 
x_train.all <- cbind(x_train, smatrix,row.names = NULL)
x_train.all <-data.frame(x_train.all)
x_train.all<-data.matrix(x_train.all)
x_train.all<-as.data.frame(x_train.all)
x_train.all<-data.matrix(x_train.all, rownames.force = NULL)
x_train.all<-x_train.all
x_train.all[,6]<-as.numeric(x_train.all[,6])
x_train.all<-as.matrix(x_train.all)
# The outcome variable
y_train.all <- train$pseudo

# Train the model

model = pseudoDNN.train(x_train.all, y_train.all)

# Predict 


#x_test<-as.data.frame(lapply(x_test, min_max_norm))
x_test<-cbind(x_test_norm,x_test[,c(1,3)])
x_test.all=do.call(rbind, replicate(length(pickTime), as.matrix(x_test), simplify=FALSE))
x_test.all<-as.data.frame(x_test.all)
s_test=rep(pickTime,each=nrow(x_test))
s_test<-as.numeric(s_test)
smatrix.test=model.matrix(~as.factor(s_test)+0)
x_test.all=cbind(x_test.all,smatrix.test)
x_test.all <-data.frame(x_test.all)
x_test.all<-data.matrix(x_test.all)
#x_test.all<-as.numeric(x_test.all)
#x_test.all$sex<-as.numeric(x_test.all$sex)


ypred.con <- pseudoDNN.predict(model, x_test.all)



# obtain the marginal survival probability by multiple series of conditional probabilities
ypred.con <- matrix(ypred.con, nrow=nrow(x_test))
ypred <- lapply(1:length(pickTime), function(i) apply(ypred.con[,1:i, drop=FALSE], 1, prod))
surv_prob <- Reduce(cbind, ypred)
head(surv_prob)
nrow(surv_prob)
max(surv_prob)
min(surv_prob)
c_i<-concordance.index(x=1-surv_prob[,1], surv.time=surv_test, surv.event=cen_test, method="noether")$c.index
valfitpbc<-(valfitpbc[[1,3]])/2+0.5 
Deep<-c(Deep, c_i)
CoxM<-c(CoxM,valfitpbc)
}

Results<-data.frame(unlist(Deep), unlist(CoxM))
boxplot(Results)
write.csv(Results,file="PBC_results.csv")
Data<-data.frame(surv_prob)
write.csv(Data, file="PBC_surv_prob.csv")
```



